Stage-Splitting a Modal Language

### 2014-10-30 paper/splitting.tex
few additions to splitting

\ur{The case for ``roll'' seems missing in partial value splitting rules.}

@@

\ur{Unclear whether the term ``masking'' includes the case for
  functions or not.  If it does, then it sounds rather
  inaccurate.  If not, then it should be stated clearly that it does
  not, but then what is the value of introducing one more term?}

@@

The splitting rule for \texttt{mono} is more difficult.
...
transition to dummy.

@@

The basic idea here is that dummy will dynamically be whatever data structure you want it to be.

This is safe because [nico is just throwing something out here] 
it can only appear in the resumers of terms that have no circles in their \lang\ type.
Since the $\prev$ rule requires a circle type, dummy values cannot leak from
the resumers of stage \bbone\ terms into the resumers of stage \bbtwo\ terms.

>>>>

@@

@@

The splitting rule for \texttt{mono} is more difficult.
The problem is that the rules needs to produce a resumer with the correct shape
for whatever the type of the \texttt{mono} is.
This is difficult in the presence of sums and general recursion,
and so we introduce a new value in our target language called dummy.
Dummy can only appear in resumers and dynamically takes the shape of whatever is required of it.

@@

Coming back to \texttt{mono}, the splitting rule is:
\begin{mathpar}
\infer{\splitone{\monoSt~e}A {e', {\tt dummy}} }{e \overset{C}{\rightarrow} e'} \and
\infer{e_1~e_2 \overset{C}{\rightarrow} \pio~(e_1'~e_2')}{e_1 \overset{C}{\rightarrow} e_1' & e_2 \overset{C}{\rightarrow} e_2'} \and
\infer{\lambda x.e \overset{C}{\rightarrow} \lambda x.(e',())}{e \overset{C}{\rightarrow} e'}
\end{mathpar}
And $\overset{C}{\rightarrow}$ operates like a map at all other terms.

Our use of {\tt dummy} is safe because
it can only appear in the resumers of terms that have no circles in their \lang\ type.
Since the $\prev$ rule requires a circle type, dummy values cannot leak from
the resumers of stage \bbone\ terms into the resumers of stage \bbtwo\ terms.
